Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2018-12-06 ms.tex
replaced the run104 plots with a longer time series.

There are two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
\begin{enumerate}
	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
	\item That the lamp is variable on short time scales of a frame (10.74 seconds).\label{item:lampReasonCV3subFull}
\end{enumerate}
The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^-1 \approx 930 $DN.
This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).
Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm. {\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should correct to 20 groups)}}
This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
However, if there are correlated components to the read noise in this large aperture, the read noise could be higher.

@@

\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization.
}\label{fig:GLtSeries}
\end{figure*}

>>>>

There are two explanations for why the WLP8SUB mode shows less scatter than the FULL modes, 
\begin{enumerate}[noitemsep]
	\item The reduction of read noise improves the stability of the signal and\label{item:readNReasonCV3subFull}
	\item That the lamp is variable on short time scales of a frame (10.74 seconds).\label{item:lampReasonCV3subFull}
\end{enumerate}
The read noise of a pixel is $RN_1 \approx$ 15 e$^-$ for the short wavelength arrays\footnote{https://jwst-docs.stsci.edu/display/JTI/NIRCam+Detector+Performance} in this test.
If this is uncorrelated across the 70 pixel aperture source radius, the read noise from two groups  (correlated double sampling) on the total aperture is $RN_{tot} = \sqrt{N_{s,px}} RN_{CDS} = \sqrt{\pi} r_{s,px} RN_{CDS}$ = 124 * 15 e$^-$ = 1861 e$^-1 \approx 930 $DN.
This amounts to 25 ppm, which is a small compared to the photon noise (113 ppm).
Furthermore, the read noise for 20 groups is $RN_{20} \approx 6e^-$ would ammount to a 10 ppm, so a difference from the CDS readout of only 15 ppm. {\textbf{\textcolor{red}{(Note, here I have used the effectice read noise for 90 groups on JDox, but should correct to 20 groups)}}
This is dramatically smaller than the observed difference in standard deviation (500 ppm in subarray with 20 groups and 1020-1540 ppm in full frame in 2 groups).
However, if there are correlated components to the read noise in this large aperture, the read noise could be higher.

@@

\begin{figure*}
\gridline{\fig{ap_labels_S02illum_GLrun104.pdf}{0.32\textwidth}{Apertures}
		\fig{raw_tser_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Raw time series}
		\fig{refcor_phot_S02illum1miAll_GLrun104.pdf}{0.32\textwidth}{Ratio Time Series}}
\caption{The precision of this short-duration GL dewar test was the extremely high at $\sigma=$240 ppm after stabilization.
}\label{fig:GLtSeries}
\end{figure*}
